Supplementary Information

### 2025-05-10 Paper/Source/manuscript.tex
Finalize first draft (except figure)

All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256 GB RAM, and 2 NVIDIA GPU (GeForce RTX 4090) with 24 GB VRAM each. All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}. Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file. Initial structures, configuration files, and command-line codes for the simulations are publicly available at... [ONLINE DATABASE TO BE PREPARED].

@@

Describe and discuss Figure~\ref{fig:hydrophobicity} (surface hydrophobicity).

@@

The hydrophobic portions of the protein surface are represented in yellow (Figure 5). In the native proteins, there are large hydrophobic patches in the transmembrane domains, which are embedded within the lipid bilayer. The nonpolar and hydrophobic amino acids including leucine (L), isoleucine (I), valine (V), phenylalanine (F), alanine (A), methionine (M), and tryptophan (W) interact with the hydrophobic hydrocarbon chains and expel water.

@@

\section*{Supplementary Material}

The supplementary material can be found at... [TO BE ADDED]

@@

The data for... can be found at... [ONLINE DATABASE TO BE PREPARED]

@@

\section*{Acknowledgments}

Thanks to... for... [TO BE ADDED]

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/function-conformation.jpg}
	\caption{\textbf{The conformational changes of native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore, retinal. } \textbf{a)} and \textbf{b)}: 1ns running averages of the root mean square distances (RMSD) of the protein-retinal complex, transmembrane helix 6 (TM6), the retinal-binding pocket, and retinal. \textbf{c)}: superpositions between cis-state OPN2, trans-state OPN2, cis-state OPN2$^{\textrm{QTY}}$, and trans-state OPN2$^{\textrm{QTY}}$. Blue: cis-state protein, orange: 11-cis-retinal; yellow: trans-state protein, greenish cyan: all-trans retinal. }
	\label{fig:conformation}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/function-binding.jpg}
	\caption{\textbf{Changes in the retinal-binding pocket and protein-ligand interaction in native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore. } \textbf{a)} and \textbf{b)}: close-ups of the binding pocket in cis-state. Blue: protein residues, orange: 11-cis-retinal; dashed lines: same as a) and b). \textbf{c)} and \textbf{d)}: close-ups of the binding pocket in trans-state. Yellow: protein residues, greenish cyan: all-trans-retinal; green dashed lines: ion bridge; yellow dashed lines: van der Waals and/or hydrophobic interactions. \textbf{e)} and \textbf{f)}: the interaction energies between the protein, the binding pocket, individual residues, and retinal. The interaction energy is the sum of the short-range Coulombic interaction energy and short-range Lennard-Jones energy. Please note that the interaction energy is a product of MD simulation and is not necessarily a meaningful physical quantity. \textbf{g)} and \textbf{h)}: the number of hydrogen bonds formed between residues in the binding pocket, and the number of water molecules within the binding pocket. }
	\label{fig:binding}
\end{figure}

>>>>

All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256 GB RAM, and 2 NVIDIA GPU (GeForce RTX 4090) with 24 GB VRAM each. All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}. Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file. Initial structures, configuration files, and command-line codes for the simulations are publicly available on Zenodo (\url{https://doi.org/10.5281/zenodo.15377505}).

@@

@@

The hydrophobic portions of the protein surface are represented in yellow (Figure~\ref{fig:hydrophobicity}). In the native proteins, there are large hydrophobic patches in the transmembrane domains, which are embedded within the lipid bilayer. The nonpolar and hydrophobic amino acids including leucine (L), isoleucine (I), valine (V), phenylalanine (F), alanine (A), methionine (M), and tryptophan (W) interact with the hydrophobic hydrocarbon chains and expel water.

@@

@@

The data for the AlphaFold3-predicted structures and MD simulation setting files and commands can be found on Zenodo (\url{https://doi.org/10.5281/zenodo.15377505}).

@@

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/function-conformation.jpg}
	\caption{\textbf{The conformational changes of native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore, retinal. } \textbf{a)} and \textbf{b)}: 1ns running averages of the root mean square distances (RMSD) of the protein-retinal complex, transmembrane helix 6 (TM6), the retinal-binding pocket, and retinal. By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line. \textbf{c)}: superpositions between cis-state OPN2, trans-state OPN2, cis-state OPN2$^{\textrm{QTY}}$, and trans-state OPN2$^{\textrm{QTY}}$. Blue: cis-state protein, orange: 11-cis-retinal; yellow: trans-state protein, greenish cyan: all-trans retinal. }
	\label{fig:conformation}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{Figures/function-binding.jpg}
\end{figure}

\begin{figure}[htbp]
	\caption{\textbf{Changes in the retinal-binding pocket and protein-ligand interaction in native OPN2 and its QTY analog before and after 11-cis to all-trans isomerization of the chromophore. } \textbf{a)} and \textbf{b)}: close-ups of the binding pocket in cis-state. Blue: protein residues, orange: 11-cis-retinal; dashed lines: same as a) and b). \textbf{c)} and \textbf{d)}: close-ups of the binding pocket in trans-state. Yellow: protein residues, greenish cyan: all-trans-retinal; green dashed lines: ion bridge; yellow dashed lines: van der Waals and/or hydrophobic interactions. \textbf{e)} and \textbf{f)}: the interaction energies between the protein, the binding pocket, individual residues, and retinal. The interaction energy is the sum of the short-range Coulombic interaction energy and short-range Lennard-Jones energy. Please note that the interaction energy is a product of MD simulation and is not necessarily a meaningful physical quantity. \textbf{g)} and \textbf{h)}: the number of hydrogen bonds formed between residues in the binding pocket, and the number of water molecules within the binding pocket. By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line. }
	\label{fig:binding}
\end{figure}

### 2025-05-10 Paper/Source/supp.tex
Write results and discussion
Finalize first draft (except figure)

\begin{figure}[H]
    \label{tb:sequence}
    \caption{\textbf{The enlarge protein sequence alignments of 12 retinylidene proteins with their water-soluble QTY analogs from Figure 1.} The symbols $|$ and $*$ indicate that amino acids are identical and different respectively. Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively. The alpha helices (blue) are shown above the protein sequences. \\
    The alignments are: 
    \textbf{a)} OPN1MW vs. OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW vs. OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW vs. OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 vs. OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 vs. OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 vs. OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 vs. OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR vs. RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH vs. RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR vs. BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH vs. BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 vs. ChR2$^{\textrm{QTY}}$. }
    \textbf{a)} OPN1MW vs. OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1mw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{b)} OPN1LW vs. OPN1LW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1lw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{c)} OPN1SW vs. OPN1SW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1sw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{d)} OPN2 vs. OPN2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn2.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{e)} OPN3 vs. OPN3$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn3.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{f)} OPN4 vs. OPN4$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn4.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{g)} OPN5 vs. OPN5$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn5.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{h)} RGR vs. RGR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/rgr.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{i)} RRH vs. RRH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/rrh.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{j)} BACR vs. BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/bacr.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{k)} BACH vs. BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/bach.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{l)} ChR2 vs. ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/chr2.jpg}
\end{figure}

\begin{figure}[H]
    \label{tb:af3}
    \caption{\textbf{AlphaFold3 prediction accuracy: plDDT, PAE, ipTM, and pTM scores.} \\
    The scores are displayed for the following proteins: 
    \textbf{a)} OPN1MW$^{\textrm{QTY}}$,
    \textbf{b)} OPN1LW$^{\textrm{QTY}}$,
    \textbf{c)} OPN1SW$^{\textrm{QTY}}$,
    \textbf{d)} OPN2$^{\textrm{QTY}}$,
    \textbf{e)} OPN3$^{\textrm{QTY}}$,
    \textbf{f)} OPN4$^{\textrm{QTY}}$,
    \textbf{g)} OPN5$^{\textrm{QTY}}$,
    \textbf{h)} RGR$^{\textrm{QTY}}$,
    \textbf{i)} RRH$^{\textrm{QTY}}$,
    \textbf{j)} BACR$^{\textrm{QTY}}$ monomer,
    \textbf{k)} BACH$^{\textrm{QTY}}$ monomer,
    \textbf{l)} ChR2$^{\textrm{QTY}}$ monomer,
    \textbf{m)} BACR$^{\textrm{QTY}}$ trimer,
    \textbf{n)} BACH$^{\textrm{QTY}}$ trimer,
    \textbf{o)} ChR2$^{\textrm{QTY}}$ dimer.}
    \textbf{a)} OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn1mw qty.jpg}
\end{figure}

@@

>>>>

\begin{figure}[H]
    \caption{\textbf{The enlarge protein sequence alignments of 12 retinylidene proteins with their water-soluble QTY analogs from Figure 1.} The symbols $|$ and $*$ indicate that amino acids are identical and different respectively. Amino acids L, V, I and F in TM (transmembrane) alpha helices are replaced with Q, T, Y and Y respectively. The alpha helices (blue) are shown above the protein sequences. \\
    The alignments are: 
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$, 
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$, 
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$, 
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$, 
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$, 
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$, 
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$, 
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$, 
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$, 
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$, 
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$, 
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$. }
    \textbf{a)} OPN1MW \textit{vs} OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1mw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{b)} OPN1LW \textit{vs} OPN1LW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1lw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{c)} OPN1SW \textit{vs} OPN1SW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn1sw.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{d)} OPN2 \textit{vs} OPN2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn2.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{e)} OPN3 \textit{vs} OPN3$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn3.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{f)} OPN4 \textit{vs} OPN4$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn4.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{g)} OPN5 \textit{vs} OPN5$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/opn5.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{h)} RGR \textit{vs} RGR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/rgr.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{i)} RRH \textit{vs} RRH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/rrh.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{j)} BACR \textit{vs} BACR$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/bacr.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{k)} BACH \textit{vs} BACH$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/bach.jpg}
\end{figure}

\newpage
\begin{figure}[H]
    \textbf{l)} ChR2 \textit{vs} ChR2$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/chr2.jpg}
\end{figure}

\begin{figure}[H]
    \caption{\textbf{AlphaFold3 prediction accuracy: plDDT, PAE, ipTM, and pTM scores.} \\
    The scores are displayed for the following proteins: 
    \textbf{a)} OPN1MW$^{\textrm{QTY}}$,
    \textbf{b)} OPN1LW$^{\textrm{QTY}}$,
    \textbf{c)} OPN1SW$^{\textrm{QTY}}$,
    \textbf{d)} OPN2$^{\textrm{QTY}}$,
    \textbf{e)} OPN3$^{\textrm{QTY}}$,
    \textbf{f)} OPN4$^{\textrm{QTY}}$,
    \textbf{g)} OPN5$^{\textrm{QTY}}$,
    \textbf{h)} RGR$^{\textrm{QTY}}$,
    \textbf{i)} RRH$^{\textrm{QTY}}$,
    \textbf{j)} BACR$^{\textrm{QTY}}$ monomer,
    \textbf{k)} BACH$^{\textrm{QTY}}$ monomer,
    \textbf{l)} ChR2$^{\textrm{QTY}}$ monomer,
    \textbf{m)} BACR$^{\textrm{QTY}}$ trimer,
    \textbf{n)} BACH$^{\textrm{QTY}}$ trimer,
    \textbf{o)} ChR2$^{\textrm{QTY}}$ dimer.}
    \textbf{a)} OPN1MW$^{\textrm{QTY}}$ \\
    \includegraphics[width=\linewidth]{SuppFigures/af3 opn1mw qty.jpg}
\end{figure}

@@

\begin{figure}[H]
    \caption{\textbf{The radius of gyration of native and QTY-designed OPN2. } By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line. The radius of gyration and its 1-ns running average are shown, respectively, as black and red lines. }
    \textbf{a)} Native OPN2 \\ \\
    \includegraphics[width=\linewidth]{SuppFigures/wt gyrate.jpg}
    \textbf{b)} QTY-designed OPN2 \\ \\
    \includegraphics[width=\linewidth]{SuppFigures/qty gyrate.jpg}
\end{figure}

\begin{figure}[H]
    \caption{\textbf{The root mean square (RMS) fluctuation of native and QTY-designed OPN2. } Blue bars represent proteins with 11-cis-retinal and yellow bars represent proteins with all-trans-retinal. The two states are plotted on the same set of axis, with the shorter bars placed on top of the taller bars. }
    \textbf{a)} Native OPN2 \\ \\
    \includegraphics[width=\linewidth]{SuppFigures/wt rmsf.jpg}
    \textbf{b)} QTY-designed OPN2 \\ \\
    \includegraphics[width=\linewidth]{SuppFigures/qty rmsf.jpg}
\end{figure}

\begin{figure}[H]
    \caption{\textbf{The root mean square distance (RMSD) of each residue in the retinal-binding pocket of native and QTY-designed OPN2. } By convention, the isomerization is set at time 0ns, which is indicated by a brown, vertical dashed line. Only the 1-ns running average of RMSD are shown for clarity. }
    \textbf{a)} Native OPN2 \\ \\
    \includegraphics[width=\linewidth]{SuppFigures/wt rmsd byres.jpg}
    \textbf{b)} QTY-designed OPN2 \\ \\
    \includegraphics[width=\linewidth]{SuppFigures/qty rmsd byres.jpg}

    \vspace{0.5cm}
    \includegraphics[width=\linewidth]{SuppFigures/legend rmsd byres.jpg}
\end{figure}
